Arrows for Parallel Computations

### 2017-05-17 paper/content/topologySkeletons.tex
renamed fig references for |***| |&&&| and |>>>| so that they work with lhs2TeX

Note that extensive use of this combinator over \inlinecode{pipe} with a hand-written combination data type will probably result in worse performance because of more communication overhead from the many calls to parEvalN. Nonetheless, we can define a parallel piping operator \inlinecode{(|>>>|)} (Fig.~\ref{fig:|>>>|}, which is semantically equivalent to \inlinecode{(>>>)} in a similar manner to the other parallel syntactic sugar from section~\ref{syntacticSugar}.
\begin{figure}[h]
\begin{lstlisting}[frame=htrbl]
(|>>>|) :: (ArrowLoop arr, ArrowChoice arr,
	ArrowParallel arr (fut (([a], [b]), [c])) (fut (([a], [b]), [c])) (),
	Future fut (([a], [b]), [c])) =>
	arr a b -> arr b c -> arr a c
(|>>>|) = pipe2 ()
\end{lstlisting}
\caption{Definition of \texttt{(|>>>|)}}
\label{fig:|>>>|}
\end{figure}

>>>>

Note that extensive use of this combinator over \inlinecode{pipe} with a hand-written combination data type will probably result in worse performance because of more communication overhead from the many calls to parEvalN. Nonetheless, we can define a parallel piping operator \inlinecode{(|>>>|)} (Fig.~\ref{fig:par>>>}, which is semantically equivalent to \inlinecode{(>>>)} in a similar manner to the other parallel syntactic sugar from section~\ref{syntacticSugar}.
\begin{figure}[h]
\begin{lstlisting}[frame=htrbl]
(|>>>|) :: (ArrowLoop arr, ArrowChoice arr,
	ArrowParallel arr (fut (([a], [b]), [c])) (fut (([a], [b]), [c])) (),
	Future fut (([a], [b]), [c])) =>
	arr a b -> arr b c -> arr a c
(|>>>|) = pipe2 ()
\end{lstlisting}
\caption{Definition of \texttt{(|>>>|)}}
\label{fig:par>>>}
\end{figure}
